---
title: "Errata for *Adaptive Experimental Design: Prospects and Applications in Political Science*"
format:
  pdf:
    output-file: offer-westort_coppock_green_2021_errata.pdf
    geometry: margin=1in
    fontsize: 11pt
---

```{r}
#| label: setup
#| include: false
library(here)
library(tidyverse)
here::i_am("errata.qmd")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

out <- function(file) {
  read_csv(here::here("maintained", "output", file), show_col_types = FALSE)
}

figure_3 <- out("figure_3_study1_posterior_probs.csv")
figure_4 <- out("figure_4_study1_mean_outcomes.csv")
figure_6 <- out("figure_6_study2_ate_estimates.csv")
static_simulations <- out("text_study1_static_simulations.csv")

mw_final <- figure_3 |>
  filter(topic == "Minimum wage", batch == 10) |>
  arrange(desc(posterior_prob))

mw_mean <- function(arm_label) {
  figure_4$estimate[figure_4$topic == "Minimum wage" & figure_4$arm == arm_label]
}

mw_p3y <- figure_3 |>
  filter(topic == "Minimum wage", arm == "Proposal 3 (Y)", batch == 10)

republican_ipw <- figure_6 |> filter(type == "Republicans", Estimates == "IPW")
lottery <- republican_ipw |> filter(term == "Lottery")
accuracy <- republican_ipw |> filter(term == "Accuracy")

mw_static <- static_simulations |> filter(topic == "Minimum wage")

fmt <- function(x, digits) sprintf(paste0("%.", digits, "f"), x)

count_word <- function(n) {
  words <- c("One", "Two", "Three", "Four", "Five", "Six", "Seven", "Eight", "Nine", "Ten")
  if (n <= length(words)) words[n] else as.character(n)
}
```

```{r}
#| label: entries
# THE ERRATA SPINE. Every entry is defined once, here, and the document below is rendered
# from it rather than from prose typed a second time. The same rows are written to
# errata_entries.csv at the foot of this file, so any other document that needs the
# corrections (the README, a remastered edition) reads them instead of keeping its own copy,
# which is how two statements of one correction come to disagree.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a published or corrected field is markup, so
# either renderer can set the same string.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been cited
# by its number, so a later finding is added at the end and never interleaved, renumbered,
# merged or split.
#
# `form` is a renderer's choice of macro for the entry: "full" where the published and
# corrected fields are whole sentences that need setting as blocks, "brief" where the entry
# is a token replacement.
#
# Every corrected value is computed here, at render time, from the maintained pipeline's
# output. None of them is typed.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "quantity", "pipeline", "full",
  "The estimated mean of the leading minimum wage arm",
  "published p. 835",
  "The winning arm, by a hair, was Proposal 3 ([[B]], without current minimum wage), with a probability of being best of 0.219 and an estimated mean of [[0.895]] over 183 respondents.",
  str_glue(
    "The winning arm, by a hair, was Proposal 3 ([[N]], without current minimum wage), with ",
    "a probability of being best of 0.219 and an estimated mean of ",
    "[[{fmt(mw_mean(mw_final$arm[1]), 3)}]] over 183 respondents."),
  str_glue(
    "The arm with a {fmt(mw_final$posterior_prob[1], 3)} probability of being best and ",
    "{mw_final$cumulative_trials[1]} respondents is Proposal 3 (N), whose ",
    "inverse-probability-weighted mean is {fmt(mw_mean('Proposal 3 (N)'), 3)}. The 0.895 ",
    "printed in the sentence is Figure 4's estimate for Proposal 3 (Y), a different arm, ",
    "which drew {mw_p3y$cumulative_trials} respondents and ended with a ",
    "{fmt(mw_p3y$posterior_prob, 3)} probability of being best. Figures 3 and 4 label the ",
    "two versions of each minimum wage proposal \"(Y)\" and \"(N)\", so the \"B\" in the ",
    "parenthesis is also an \"N\"."),

  2, "label", "pipeline", "full",
  "The arm carrying the 4.1-point Republican effect",
  "published p. 840",
  "In this particular case, the adaptive design with the smaller standard error allows us to declare the 4.1-point average effect of the [[accuracy]] treatment statistically significant (p = 0.014), whereas under that static design the effect would not have attained statistical significance (p = 0.152).",
  str_glue(
    "In this particular case, the adaptive design with the smaller standard error allows us ",
    "to declare the {fmt(100 * lottery$estimate, 1)}-point average effect of the ",
    "[[Lottery]] treatment statistically significant (p = {fmt(lottery$p.value, 3)}), ",
    "whereas under that static design the effect would not have attained statistical ",
    "significance (p = 0.152)."),
  str_glue(
    "Figure 6 gives the Republican Lottery arm an effect of ",
    "{fmt(100 * lottery$estimate, 1)} percentage points with a p-value of ",
    "{fmt(lottery$p.value, 3)}. The Accuracy arm's Republican estimate is ",
    "{fmt(100 * accuracy$estimate, 1)} percentage points, in the opposite direction, with a ",
    "p-value of {fmt(accuracy$p.value, 3)}. The two preceding sentences and Figure 5 both ",
    "identify the Lottery as the arm in question. The static-design p-value of 0.152 is ",
    "left as printed: it comes from a bootstrap the deposited materials do not seed ",
    "reproducibly, and the reproduction cannot recompute it."),

  3, "quantity", "pipeline", "full",
  "The share of static minimum wage simulations picking the best proposal",
  "published p. 837",
  "Treating observed success rates as the truth in simulations of the minimum wage experiment, we picked the best proposal 47% of the time in adaptive experiments and [[37%]] of the time in static experiments.",
  str_glue(
    "Treating observed success rates as the truth in simulations of the minimum wage ",
    "experiment, we picked the best proposal ",
    "{fmt(100 * mw_static$correct_adaptive, 0)}% of the time in adaptive experiments and ",
    "[[{fmt(100 * mw_static$correct_static, 1)}%]] of the time in static experiments."),
  str_glue(
    "The deposited simulations pick the best minimum wage proposal in ",
    "{fmt(100 * mw_static$correct_static, 2)} per cent of ",
    "{format(mw_static$iterations, big.mark = ',')} static runs, which is ",
    "{fmt(100 * mw_static$correct_static, 0)} per cent at the whole-percentage precision ",
    "the sentence uses. Rounding to one decimal first gives 36.5, and rounding that again ",
    "gives 37. The other three shares in the same passage round correctly."),

  4, "bibliographic", "reference_audit", "brief",
  "Pallmann et al. (2018) skips its ninth author and runs two words of its title together",
  "published p. 844",
  paste(
    "Pallmann, Philip, Alun W. Bedding, Babak Choodari-Oskooei, Munyaradzi Dimairo, Laura ",
    "Flight, Lisa V. Hampson, Jane Holmes, Adrian P. Mander, Matthew R. Sydes, Sofía S. ",
    "Villar, et al. 2018. \"Adaptive Designs in Clinical Trials: Why [[UseThem]], and How ",
    "to Run and Report Them.\" BMC Medicine 16(1): 29."),
  paste(
    "Pallmann, Philip, Alun W. Bedding, Babak Choodari-Oskooei, Munyaradzi Dimairo, Laura ",
    "Flight, Lisa V. Hampson, Jane Holmes, Adrian P. Mander, [[Lang'o Odondi]], Matthew R. ",
    "Sydes, Sofía S. Villar, et al. 2018. \"Adaptive Designs in Clinical Trials: Why [[Use ",
    "Them]], and How to Run and Report Them.\" BMC Medicine 16(1): 29."),
  paste(
    "Two defects in one entry. The names it prints ninth and tenth are the article's tenth",
    "and eleventh authors: Lang'o Odondi is skipped, so the entry is not the first ten",
    "authors of anything. Crossref, doi 10.1186/s12916-018-1017-7: Pallmann, Bedding,",
    "Choodari-Oskooei, Dimairo, Flight, Hampson, Holmes, Mander, Odondi, Sydes, Villar,",
    "Wason, Weir, Wheeler, Yap, Jaki. The insertion is marked on the corrected side only,",
    "since no span of the published list is wrong in itself. The title's \"Use Them\" is set",
    "without its space, which the rendered page confirms rather than the text extraction.")
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

`r count_word(nrow(entries))` corrections to Offer-Westort, Coppock, and Green (2021), *American Journal of Political Science* 65(4): 826–844, [doi:10.1111/ajps.12597](https://doi.org/10.1111/ajps.12597). `r count_word(sum(entries$class != "bibliographic"))` are sentences stating a number or a treatment label that the study's own data do not support, and `r tolower(count_word(sum(entries$class == "bibliographic")))` is a reference-list entry. No conclusion in the article changes, and every figure and table it reports is correct as printed. The corrected values in entries 1 to `r max(entries$entry[entries$class != "bibliographic"])` are computed from a maintained reproduction of the analysis, held at `active-maintenance-aec/offer-westort_coppock_green_2021`, which reproduces all 913 of the article's published table and figure values; the reference-list entry is verified against the authoritative record at Crossref, named in the entry.

Changed tokens are shown in bold on both sides. Where a sentence contains other quantities, those are reprinted unchanged.

```{r}
#| label: render-entries
#| results: asis
# A heading is only a heading when a blank line precedes it: emitted straight after the
# previous entry's note, "## 2." lands in the page as literal text.
walk(seq_len(nrow(entries)), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", e$title,
      "\n\n> ", bold(e$published), " (", str_remove(e$location, "^published "), ")",
      "\n\n*Corrected:* ", bold(e$corrected),
      "\n\n", e$note, "\n", sep = "")
})
```

```{r}
#| label: emit-spine
# The machine-readable spine, written wherever this document is rendered. Every other
# statement of these corrections reads it rather than restating them.
write_csv(entries, here("errata_entries.csv"))
```
